Evolution of precopulatory and postcopulatory inbreeding behaviour

### 2016-09-07 ms_pre_post.Rmd
Add start of table

---
title: "Evolution of precopulatory and postcopulatory inbreeding behaviour"
author: "A. Bradley Duthie et al."
date: "August 24, 2016"
output:
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
  pdf_document:
    fig_caption: yes
  html_document: default
header-includes:
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 1
csl: evolution.csl
bibliography: ms_pre_post.bib
---

@@

>>>>

---
title: "Evolution of precopulatory and postcopulatory inbreeding behaviour"
author: "A. Bradley Duthie et al."
date: "August 24, 2016"
output:
  pdf_document:
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
header-includes:
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 1
csl: evolution.csl
bibliography: ms_pre_post.bib
---

@@

Table 1
----------------------------------------------

|-----|---------------------------------------|-------------|---------------|--------------
| **A** | **Trait**                           | **Allele**  | **Genotype**  | **Phenotype**
|       | Tendency for polyandry              | $P_{a}$     | $P_{g}$       | $P_{p}$
|       | Inbreeding mating strategy          | $M_{a}$     | $M_{g}$       | $M_{p}$
|       | Inbreeding fertilisation strategy   | $F_{a}$     | $F_{g}$       | $F_{p}$
|       |                                     |             |               |
| **B** | **Description**                     | **Parameter**  | | **Defaut value(s)**
